Reading episode files and preparing data sets

### 2025-11-07 data-raw/01-preprocessing-episode-files.Rmd
Updating dataset to remove duplicated instances. Updating documentation to set new version.

| **Code** | **Location** | **Year** | **Description** |
|----------------|----------------|----------------|--------------------------|
| 300 | At home or on property | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 301 | At place of work or school | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 302 | Away on business | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 303 | At someone else's home or property | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 304 | In the neighbourhood | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 305 | Outdoors | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 306 | Grocery store, other stores or mall | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 307 | Library, museum or theatre | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 308 | Sports centre, field or arena | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 309 | Restaurant, bar or club | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 310 | Place of worship | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 311 | Medical, dental or other health clinic | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 312 | Elsewhere | 2015 | Walking (code = 315) and Cycling (code = 318) to this location |
| 1 | Respondent's home | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 2 | Work place | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 3 | Someone else's home | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 4 | Restaurant/bar | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 5 | Place of worship | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 6 | Grocery store | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 7 | Other store/Mall | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 8 | School | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 9 | Outdoors away from home | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 10 | Library | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 11 | Other place | 2010 | Walking (code = 14) and Cycling (code = 17) to this location |
| 1 | Respondent's home | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 2 | Work place | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 3 | Someone else's home | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 4 | Restaurant/bar | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 5 | Place of worship | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 6 | Grocery store | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 7 | Other store/Mall | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 8 | School | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 9 | Outdoors away from home | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 10 | Library | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 11 | Other place | 2005 | Walking (code = 14) and Cycling (code = 17) to this location |
| 1 | Respondent's home | 1998 | Walking (code = 7) and Cycling (code = 9) to this location |
| 2 | Work place | 1998 | Walking (code = 7) and Cycling (code = 9) to this location |
| 3 | Someone else's home | 1998 | Walking (code = 7) and Cycling (code = 9) to this location |
| 4 | Other plourhood | 1998 | Walking (code = 7) and Cycling (code = 9) to this location |
| 1 | Respondent's home | 1992 | Walking (code = 7) and Cycling (code = 9) to this location |
| 2 | Work place | 1992 | Walking (code = 7) and Cycling (code = 9) to this location |
| 3 | Someone else's home | 1992 | Walking (code = 7) and Cycling (code = 9) to this location |
| 4 | Other place | 1992 | Walking (code = 7) and Cycling (code = 9) to this location |
| 1 | Respondent's home | 1886 | Walking (code = 5) to this location |
| 2 | Work place | 1886 | Walking (code = 5) to this location |
| 3 | At other places | 1886 | Walking (code = 5) to this location |
| 7 | other | 1886 | Walking (code = 5) to this location |

@@

```{r}
walking_2015 <- walking_2015 |>
  filter(origin <= 321) |>
  mutate(orig_label =
           case_when(origin == 300 ~ "Home", 
                     origin == 301 ~ "Work or school",
                     origin == 302 ~ "Business",
                     origin == 303 ~ "Other's home",
                     origin == 304 ~ "In the neighbourhood",
                     origin == 305 ~ "Outdoors",
                     origin == 306 ~ "Grocery store, other stores or mall",
                     origin == 307 ~ "Library, museum or theatre",
                     origin == 308 ~ "Sports centre, field or arena",
                     origin == 309 ~ "Restaurant, bar or club",
                     origin == 310 ~ "Place of worship",
                     origin == 311 ~ "Medical, dental or other health clinic",
                     origin == 312 ~ "Elsewhere",
                     origin %in% c(313,314,319) ~ "Travel - Motorized",
                     origin %in% c(317,320,321) ~ "Travel - Other",
                     origin == 316 ~ "Travel - Transit",
                     origin == 315 ~ "Travel - Walk",
                     origin == 318 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

@@

```{r}
walking_2015 <- walking_2015 |>  
  filter(destination <= 321) |>
  mutate(dest_label =
           case_when(destination == 300 ~ "Home", 
                     destination == 301 ~ "Work or school",
                     destination == 302 ~ "Business",
                     destination == 303 ~ "Other's home",
                     destination == 304 ~ "In the neighbourhood",
                     destination == 305 ~ "Outdoors",
                     destination == 306 ~ "Grocery store, other stores or mall",
                     destination == 307 ~ "Library, museum or theatre",
                     destination == 308 ~ "Sports centre, field or arena",
                     destination == 309 ~ "Restaurant, bar or club",
                     destination == 310 ~ "Place of worship",
                     destination == 311 ~ "Medical, dental or other health clinic",
                     destination == 312 ~ "Elsewhere",
                     destination %in% c(313,314,319) ~ "Travel - Motorized",
                     destination %in% c(317,320,321) ~ "Travel - Other",
                     destination == 316 ~ "Travel - Transit",
                     destination == 315 ~ "Travel - Walk",
                     destination == 318 ~ "Travel - Bycicle"),
         dest_label = factor(dest_label))
```

@@

```{r}
walking_2015 <- walking_2015 |>
  mutate(act_label = "Transport to or from activity") |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)
```

@@

```{r}
cycling_2015 <- cycling_2015 |>
  filter(origin <= 321) |>
  mutate(orig_label =
           case_when(origin == 300 ~ "Home", 
                     origin == 301 ~ "Work or school",
                     origin == 302 ~ "Business",
                     origin == 303 ~ "Other's home",
                     origin == 304 ~ "In the neighbourhood",
                     origin == 305 ~ "Outdoors",
                     origin == 306 ~ "Grocery store, other stores or mall",
                     origin == 307 ~ "Library, museum or theatre",
                     origin == 308 ~ "Sports centre, field or arena",
                     origin == 309 ~ "Restaurant, bar or club",
                     origin == 310 ~ "Place of worship",
                     origin == 311 ~ "Medical, dental or other health clinic",
                     origin == 312 ~ "Elsewhere",
                     origin %in% c(313,314,319) ~ "Travel - Motorized",
                     origin %in% c(317,320,321) ~ "Travel - Other",
                     origin == 316 ~ "Travel - Transit",
                     origin == 315 ~ "Travel - Walk",
                     origin == 318 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

@@

```{r}
# change destination and origins to text column
cycling_2015 <- cycling_2015 |>  
  filter(destination <= 321) |>
  mutate(dest_label =
           case_when(destination == 300 ~ "Home", 
                     destination == 301 ~ "Work or school",
                     destination == 302 ~ "Business",
                     destination == 303 ~ "Other's home",
                     destination == 304 ~ "In the neighbourhood",
                     destination == 305 ~ "Outdoors",
                     destination == 306 ~ "Grocery store, other stores or mall",
                     destination == 307 ~ "Library, museum or theatre",
                     destination == 308 ~ "Sports centre, field or arena",
                     destination == 309 ~ "Restaurant, bar or club",
                     destination == 310 ~ "Place of worship",
                     destination == 311 ~ "Medical, dental or other health clinic",
                     destination == 312 ~ "Elsewhere",
                     destination %in% c(313,314,319) ~ "Travel - Motorized",
                     destination %in% c(317,320,321) ~ "Travel - Other",
                     destination == 316 ~ "Travel - Transit",
                     destination == 315 ~ "Travel - Walk",
                     destination == 318 ~ "Travel - Bycicle"),
         dest_label = factor(dest_label))
```

@@

```{r}
cycling_2015 <- cycling_2015 |>
  mutate(act_label = "Transport to or from activity") |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)
```

@@

```{r}
walking_2010 <- walking_2010 |>
  filter(origin <= 21 ) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(18,20,21) ~ "Travel - Other",
                     origin %in% c(15,16) ~ "Travel - Transit",
                     origin == 14 ~ "Travel - Walk",
                     origin == 17 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

@@

```{r}
walking_2010 <- walking_2010 |>
  filter(destination <= 21 ) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(18,20,21) ~ "Travel - Other",
                     destination %in% c(15,16) ~ "Travel - Transit",
                     destination == 14 ~ "Travel - Walk",
                     destination == 17 ~ "Travel - Bycicle"),
         dest_label = factor(dest_label))
```

@@

  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)

@@

```{r}
cycling_2010 <- cycling_2010 |>
  filter(origin <= 21 ) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(18,20,21) ~ "Travel - Other",
                     origin %in% c(15,16) ~ "Travel - Transit",
                     origin == 14 ~ "Travel - Walk",
                     origin == 17 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

@@

```{r}
cycling_2010 <- cycling_2010 |>
  filter(destination <= 21 ) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(18,20,21) ~ "Travel - Other",
                     destination %in% c(15,16) ~ "Travel - Transit",
                     destination == 14 ~ "Travel - Walk",
                     destination == 17 ~ "Travel - Bycicle"),
         dest_label = factor(dest_label))
```

@@

```{r}
walking_2005 <- walking_2005 |>
  filter(origin <= 21 ) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(18,20,21) ~ "Travel - Other",
                     origin %in% c(15,16) ~ "Travel - Transit",
                     origin == 14 ~ "Travel - Walk",
                     origin == 17 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

@@

```{r}
walking_2005 <- walking_2005 |>
  filter(destination <= 21 ) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(18,20,21) ~ "Travel - Other",
                     destination %in% c(15,16) ~ "Travel - Transit",
                     destination == 14 ~ "Travel - Walk",
                     destination == 17 ~ "Travel - Bycicle"),
         dest_label = factor(dest_label))
```

@@

```{r}
cycling_2005 <- cycling_2005 |>
  filter(origin <= 21 ) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(18,20,21) ~ "Travel - Other",
                     origin %in% c(15,16) ~ "Travel - Transit",
                     origin == 14 ~ "Travel - Walk",
                     origin == 17 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

@@

```{r}
cycling_2005 <- cycling_2005 |>
  filter(destination <= 21 ) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(18,20,21) ~ "Travel - Other",
                     destination %in% c(15,16) ~ "Travel - Transit",
                     destination == 14 ~ "Travel - Walk",
                     destination == 17 ~ "Travel - Bycicle"),
         dest_label = factor(dest_label))
```

@@

```{r}
walking_1998 <- walking_1998 |>
  filter(origin <= 10 ) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin == 2 ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 4 ~ "Elsewhere",
                     origin %in% c(5,6) ~ "Travel - Motorized",
                     origin == 10 ~ "Travel - Other",
                     origin == 8  ~ "Travel - Transit",
                     origin == 7 ~ "Travel - Walk",
                     origin == 9 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

@@

```{r}
walking_1998 <- walking_1998 |>
  filter(destination <= 10 ) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination == 2 ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 4 ~ "Elsewhere",
                     destination %in% c(5,6) ~ "Travel - Motorized",
                     destination == 10 ~ "Travel - Other",
                     destination == 8  ~ "Travel - Transit",
                     destination == 7 ~ "Travel - Walk",
                     destination == 9 ~ "Travel - Bycicle"),
         dest_label = factor(dest_label))
```

@@

```{r}
cycling_1998 <- cycling_1998 |>
  filter(origin <= 10 ) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin == 2 ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 4 ~ "Elsewhere",
                     origin %in% c(5,6) ~ "Travel - Motorized",
                     origin == 10 ~ "Travel - Other",
                     origin == 8  ~ "Travel - Transit",
                     origin == 7 ~ "Travel - Walk",
                     origin == 9 ~ "Travel - Bycicle"),
         orig_label = factor(orig_label))
```

>>>>

| Origin/Destination                     | LOCATION (2022)        | LOCATION (2015) | PLACE (2010) | PLACE (2005) | PLACE (1998) | PLACE (1998) | LOCATION (1986) |
| -------------------------------------- | ---------------------- | --------------- | ------------ | ------------ | ------------ | ------------ | --------------- |
| Home                                   | 3300                   | 300             | 1            | 1            | 1            | 1            | 1               |
| Work or school                         | 3301                   | 301             | 2, 8         | 2, 8         | 2            | 2            | 2               |
| Business                               | 3302                   | 302             |              |              |              |              |                 |
| Other's home                           | 3303                   | 303             | 3            | 3            | 3            | 3            |                 |
| In the neighbourhood                   | 3304                   | 304             |              |              |              |              |                 |
| Outdoors                               | 3305                   | 305             | 9            | 9            |              |              |                 |
| Grocery store, other stores or mall    | 3306                   | 306             | 6, 7         | 6, 7         |              |              |                 |
| Library, museum or theatre             | 3307                   | 307             | 10           | 10           |              |              |                 |
| Sports centre, field or arena          | 3308                   | 308             |              |              |              |              |                 |
| Restaurant, bar or club                | 3309                   | 309             | 4            | 4            |              |              |                 |
| Place of worship                       | 3310                   | 310             | 5            | 5            |              |              |                 |
| Medical, dental or other health clinic | 3311                   | 311             |              |              |              |              |                 |
| Elsewhere                              | 3312                   | 312             | 11           | 11           | 4            | 4            | 3               |
| Travel - Motorized                     | 3313, 3314, 3319, 3320 | 313, 314, 319   | 12, 13, 19   | 12, 13, 19   | 5, 6         | 5, 6         | 4               |
| Travel - Public transit                | 3316                   | 316             | 15, 16       | 15, 16       | 8            | 8            | 6               |
| Travel - Walk                          | 3315                   | 315             | 14           | 14           | 7            | 7            | 5               |
| Travel - Bicycle                       | 3318                   | 318             | 17           | 17           | 9            | 9            |                 |
| Travel - Other                         |  3317, 3323, 3399      | 317, 320, 321   | 18, 20, 21   | 18, 20, 21   | 10           | 10           | 7               |

@@

```{r}
walking_2015 <- walking_2015 |>
  filter(!origin %in% c(315, 318, 317,320,321)) |>
  mutate(orig_label =
           case_when(origin == 300 ~ "Home", 
                     origin == 301 ~ "Work or school",
                     origin == 302 ~ "Business",
                     origin == 303 ~ "Other's home",
                     origin == 304 ~ "In the neighbourhood",
                     origin == 305 ~ "Outdoors",
                     origin == 306 ~ "Grocery store, other stores or mall",
                     origin == 307 ~ "Library, museum or theatre",
                     origin == 308 ~ "Sports centre, field or arena",
                     origin == 309 ~ "Restaurant, bar or club",
                     origin == 310 ~ "Place of worship",
                     origin == 311 ~ "Medical, dental or other health clinic",
                     origin == 312 ~ "Elsewhere",
                     origin %in% c(313,314,319) ~ "Travel - Motorized",
                     origin == 316 ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```

@@

```{r}
walking_2015 <- walking_2015 |>  
  filter(!destination %in% c(315, 318, 317,320,321)) |>
  mutate(dest_label =
           case_when(destination == 300 ~ "Home", 
                     destination == 301 ~ "Work or school",
                     destination == 302 ~ "Business",
                     destination == 303 ~ "Other's home",
                     destination == 304 ~ "In the neighbourhood",
                     destination == 305 ~ "Outdoors",
                     destination == 306 ~ "Grocery store, other stores or mall",
                     destination == 307 ~ "Library, museum or theatre",
                     destination == 308 ~ "Sports centre, field or arena",
                     destination == 309 ~ "Restaurant, bar or club",
                     destination == 310 ~ "Place of worship",
                     destination == 311 ~ "Medical, dental or other health clinic",
                     destination == 312 ~ "Elsewhere",
                     destination %in% c(313,314,319) ~ "Travel - Motorized",
                     destination == 316 ~ "Travel - Transit"),
         dest_label = factor(dest_label)) %>%   filter(!is.na(dest_label))
```

@@

```{r}
walking_2015 <- walking_2015 |>
  mutate(act_label = "Transport to or from activity") |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province) %>% 
  distinct()
```

@@

```{r}
cycling_2015 <- cycling_2015 |>
  filter(!origin %in% c(315, 318, 317,320,321)) |>
  mutate(orig_label =
           case_when(origin == 300 ~ "Home", 
                     origin == 301 ~ "Work or school",
                     origin == 302 ~ "Business",
                     origin == 303 ~ "Other's home",
                     origin == 304 ~ "In the neighbourhood",
                     origin == 305 ~ "Outdoors",
                     origin == 306 ~ "Grocery store, other stores or mall",
                     origin == 307 ~ "Library, museum or theatre",
                     origin == 308 ~ "Sports centre, field or arena",
                     origin == 309 ~ "Restaurant, bar or club",
                     origin == 310 ~ "Place of worship",
                     origin == 311 ~ "Medical, dental or other health clinic",
                     origin == 312 ~ "Elsewhere",
                     origin %in% c(313,314,319) ~ "Travel - Motorized",
                     origin == 316 ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```

@@

```{r}
# change destination and origins to text column
cycling_2015 <- cycling_2015 |>  
  filter(!destination %in% c(315, 318, 317,320,321)) |>
  mutate(dest_label =
           case_when(destination == 300 ~ "Home", 
                     destination == 301 ~ "Work or school",
                     destination == 302 ~ "Business",
                     destination == 303 ~ "Other's home",
                     destination == 304 ~ "In the neighbourhood",
                     destination == 305 ~ "Outdoors",
                     destination == 306 ~ "Grocery store, other stores or mall",
                     destination == 307 ~ "Library, museum or theatre",
                     destination == 308 ~ "Sports centre, field or arena",
                     destination == 309 ~ "Restaurant, bar or club",
                     destination == 310 ~ "Place of worship",
                     destination == 311 ~ "Medical, dental or other health clinic",
                     destination == 312 ~ "Elsewhere",
                     destination %in% c(313,314,319) ~ "Travel - Motorized",
                     destination == 316 ~ "Travel - Transit"),
         dest_label = factor(dest_label)) %>%   filter(!is.na(dest_label))
```

@@

```{r}
cycling_2015 <- cycling_2015 |>
  mutate(act_label = "Transport to or from activity") |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province) %>%    distinct()
```

@@

```{r}
walking_2010 <- walking_2010 |>
  filter(!origin %in% c(18, 20, 21, 14, 17)) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(15,16) ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```

@@

```{r}
walking_2010 <- walking_2010 |>
  filter(!destination %in% c(18, 20, 21, 14, 17)) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(15,16) ~ "Travel - Transit"),
         dest_label = factor(dest_label)) %>%   filter(!is.na(dest_label))
```

@@

  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province) %>%    distinct()

@@

```{r}
cycling_2010 <- cycling_2010 |>
  filter(!origin %in% c(18, 20, 21, 14, 17)) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(15,16) ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```

@@

```{r}
cycling_2010 <- cycling_2010 |>
  filter(!destination %in% c(18, 20, 21, 14, 17)) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(15,16) ~ "Travel - Transit"),
         dest_label = factor(dest_label)) %>%   filter(!is.na(dest_label))
```

@@

```{r}
walking_2005 <- walking_2005 |>
  filter(!origin %in% c(18, 20, 21, 14, 17)) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(15,16) ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```

@@

```{r}
walking_2005 <- walking_2005 |>
  filter(!destination %in% c(18, 20, 21, 14, 17)) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(15,16) ~ "Travel - Transit"),
         dest_label = factor(dest_label)) %>%   filter(!is.na(dest_label))
```

@@

```{r}
cycling_2005 <- cycling_2005 |>
  filter(!origin %in% c(18, 20, 21, 14, 17)) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin %in% c(2,8) ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 9 ~ "Outdoors",
                     origin %in% c(6,7) ~ "Grocery store, other stores or mall",
                     origin == 10 ~ "Library, museum or theatre",
                     origin == 4 ~ "Restaurant, bar or club",
                     origin == 5 ~ "Place of worship",
                     origin == 11 ~ "Elsewhere",
                     origin %in% c(12,13,19) ~ "Travel - Motorized",
                     origin %in% c(15,16) ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```

@@

```{r}
cycling_2005 <- cycling_2005 |>
  filter(!destination %in% c(18, 20, 21, 14, 17)) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination %in% c(2,8) ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 9 ~ "Outdoors",
                     destination %in% c(6,7) ~ "Grocery store, other stores or mall",
                     destination == 10 ~ "Library, museum or theatre",
                     destination == 4 ~ "Restaurant, bar or club",
                     destination == 5 ~ "Place of worship",
                     destination == 11 ~ "Elsewhere",
                     destination %in% c(12,13,19) ~ "Travel - Motorized",
                     destination %in% c(15,16) ~ "Travel - Transit"),
         dest_label = factor(dest_label)) %>%   filter(!is.na(dest_label))
```

@@

```{r}
walking_1998 <- walking_1998 |>
  filter(!origin %in% c(7, 9, 10)) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin == 2 ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 4 ~ "Elsewhere",
                     origin %in% c(5,6) ~ "Travel - Motorized",
                     origin == 8  ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```

@@

```{r}
walking_1998 <- walking_1998 |>
  filter(!destination %in% c(7, 9, 10)) |>
  mutate(dest_label =
           case_when(destination == 1 ~ "Home", 
                     destination == 2 ~ "Work or school",
                     destination == 3 ~ "Other's home",
                     destination == 4 ~ "Elsewhere",
                     destination %in% c(5,6) ~ "Travel - Motorized",
                     destination == 8  ~ "Travel - Transit"),
         dest_label = factor(dest_label)) %>%   filter(!is.na(dest_label))
```

@@

```{r}
cycling_1998 <- cycling_1998 |>
  filter(!origin %in% c(7, 9, 10)) |>
  mutate(orig_label =
           case_when(origin == 1 ~ "Home", 
                     origin == 2 ~ "Work or school",
                     origin == 3 ~ "Other's home",
                     origin == 4 ~ "Elsewhere",
                     origin %in% c(5,6) ~ "Travel - Motorized",
                     origin == 8  ~ "Travel - Transit"),
         orig_label = factor(orig_label)) %>%   filter(!is.na(orig_label))
```
